Binary Latent Representations for Efficient Ranking

### 2017-06-15 paper/paper.tex
Fix memory use in introduction.

To alleviate these constraints in both online and offline settings, we propose the use of binary item and user representations in learning-to-rank matrix factorization models. Following the approach of \citet{rastegari2016xnor}, we show that we can estimate binary user and item representations that achieve comparable ranking accuracy to standard learning-to-rank approaches while being several times faster to score and requiring a fraction of the memory. In MovieLens 100k experiments, our binary representations are within 4\% of the accuracy of the real-valued model, but are over 13 times faster to score and take 55\% of the memory.

>>>>

To alleviate these constraints in both online and offline settings, we propose the use of binary item and user representations in learning-to-rank matrix factorization models. Following the approach of \citet{rastegari2016xnor}, we show that we can estimate binary user and item representations that achieve comparable ranking accuracy to standard learning-to-rank approaches while being several times faster to score and requiring a fraction of the memory. In MovieLens 100k experiments, our binary representations are within 4\% of the accuracy of the real-valued model, but are over 13 times faster to score and take only 6\% of the memory.
